Yaourt pliss\'{e}, yaourt flamb\'{e}

### 2014-01-27 plis_figures.tex
scale z in the computation of the area
Label regimes x axes at bottom only

\begin{figure}
	\begin{tikzpicture}
	\begin{groupplot}[%
		group style={group name=g, group size=1 by 2},
		xmin=0, xmax=200, xtick={20,40,...,180},
		xlabel={time (min)}, 
		extra tick style={grid=major},%
		extra x tick labels={},%
		width=\columnwidth,
		height=0.5\columnwidth,
		]
	\nextgroupplot[ylabel={Relative volume}, ymin=0.3, ymax=1, extra x ticks={12.55}]
	\addplot+[no marks,Accent1] table{volume_rel_half_cas8.txt};
	\node[rotate=90, anchor=base] at (axis cs:12.55,0.75) (syn) {synæresis};
	\node[right=0 of syn.south west] {swelling};

	\nextgroupplot[ylabel={Excess area (\%)}, ymin=0, ymax=4, extra x ticks={26.7, 42.8}]
	\addplot+[no marks,Accent1] table{excess_area_pc_half_cas8.txt};
	\end{groupplot}

>>>>

\begin{figure}
	\begin{tikzpicture}
	\begin{groupplot}[%
		group style={
			group name=g, group size=1 by 2,
			xticklabels at=edge bottom,
			vertical sep=0,
			},
		xmin=0, xmax=200, xtick={20,40,...,180},
		extra tick style={grid=major},%
		extra x tick labels={},%
		width=\columnwidth,
		height=0.5\columnwidth,
		]
	\nextgroupplot[ylabel={Rel. volume}, ymin=0.3, ymax=1, extra x ticks={12.55}]
	\addplot+[no marks,Accent1] table{volume_rel_half_cas8.txt};
	\node[rotate=90, anchor=base] at (axis cs:12.55,0.75) (syn) {synæresis};
	\node[above right=0 of syn.south west] {swelling};

	\nextgroupplot[ylabel={Excess area (\%)}, ymin=0, ymax=1.2, xlabel={time (min)}, extra x ticks={26.7, 42.8}]
	\addplot+[no marks,Accent1] table{excess_area_pc_half_cas8.txt};
	\node at (axis cs:13.35,1) {flat};
	\node[rotate=90, anchor=east] at (axis cs:34.75,1) {wrinkling};
	\node[anchor=west] at (axis cs:45,0.25) {wrinkling and buckling};
	\end{groupplot}
